\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-10-03 NAR_DRAFT.tex
supplementary figures
zenodo id

\section{Software Availability}
\bkmcomment{working on this today}

github for source code

zenodo for figures, simulations

zenodo for package at time of bioarxiv

@@

\begin{figure}[b]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/fig_wgs.png}
  \end{center}
  \caption{Model performance on 100X simulated whole genome.
  \textbf{(A)} Precision recall curves and \textbf{(B)} Reciever operating characteristic curves for 3 mutation profiles.
  Distribution of estimated true positive probabilities for true positive  variants for \textbf{(C)} the MuTect model and \textbf{(D))} the \batcave model.
  A perfectly calibrated model would generate the diagonal line.}
\label{NAR-wgs_fig}
\end{figure}

\clearpage
\begin{figure}
  \begin{center}
  \includegraphics{figures/ppv_wgs.pdf}
  \end{center}
  \caption{Model performance on 100X simulated whole genome. 
  Positive predictive values vs. Recall for five different probability cutoffs. 
  Note the restricted axes to improve readability of points.}
\label{NAR-ppv_wgs_fig}
\end{figure}

>>>>

\section{Software Availability}

The \texttt{batcaver} R package can be downloaded or installed from \texttt{github.com/bmannakee/batcaver}
The version of \texttt{batcaver} used to generate results, and all analysis code have been preserved on Zenodo \texttt{https://doi.org/10.5281/zenodo.3471715}

@@

\begin{figure}[b]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/fig_wgs.pdf}
  \end{center}
  \caption{Model performance on 100X simulated whole genome.
  \textbf{(A)} Precision recall curves and \textbf{(B)} Reciever operating characteristic curves for 3 mutation profiles.
  Distribution of estimated true positive probabilities for true positive  variants for \textbf{(C)} the MuTect model and \textbf{(D))} the \batcave model.
  A perfectly calibrated model would generate the diagonal line.}
\label{NAR-wgs_fig}
\end{figure}

\clearpage
\begin{figure}
  \begin{center}
  \includegraphics{figures/ppv_wgs.pdf}
  \end{center}
  \caption{Model performance on 100X simulated whole genome. 
  Precision vs. Recall for five different probability cutoffs. 
  Note the restricted axes to improve readability of points.}
\label{NAR-ppv_wgs_fig}
\end{figure}
